The Rockerverse: Packages and Applications for Containerisation with R

### 2020-02-05 manuscript.Rmd
add conclusion summary to abstract, give examples for use cases

  These use cases and the variety of applications demonstrate the power of Rocker specifically and containerisation in general.

@@

>>>>

  These use cases cover diverse topics such as package development, reproducible research, collaborative work, cloud-based data processing, and production deployment of services.
  The variety of applications demonstrates the power of Rocker specifically and containerisation in general.

@@

  We conclude that the current growth and diversification of use cases is likely to continue its positive impact, but see the need for consolidating the Rockerverse ecosystem of packages, developing common practices for applications, and exploring alternative containerisation software.
